Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2018-11-02 analysis/paper/paper.Rmd
Fix "kgkg / ^"

kable(N_rates,
      caption = "Nitrogen application rates for 2015 and 2016. Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180). Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications.")
```

@@

```{r fig-2, fig.cap="Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180). Points represent the mean observations of four replications."}

@@

##### Tiller sheath blight incidence boxplot for N rate
```{r fig-4, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid--point percentage value to calculate the AUDPS. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180)."}

@@

```{r fig-5, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on sheath blight tiller incidence and tiller severity. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180)."}

@@

```{r fig-6, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on sheath blight leaf severity. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kgkg&nbsp;/^&nbsp;ha N (N100) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kgkg&nbsp;/^&nbsp;ha N (N60) and 180&nbsp;kgkg&nbsp;/^&nbsp;ha N (N180)."}

>>>>

kable(N_rates,
      caption = "Nitrogen application rates for 2015 and 2016. Five different nitrogen treatments were applied depending on the experiment. In the 2015 experiment three nitrogen rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120). In the 2016 experiment, two nitrogen rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180). Treatments in both years were applied in splits at: basal, tillering growth stages for all treatments and panicle initiation growth stage for treatments with three applications.")
```

@@

```{r fig-2, fig.cap="Sheath blight incidence progress was measured in the 2015 experiment at five assessment points and 2016 experiment at four assessment points during the dry season both years. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180). Points represent the mean observations of four replications."}

@@

##### Tiller sheath blight incidence boxplot for N rate
```{r fig-4, fig.cap="Sheath blight severity progress was measured in the 2015 at five assessment points and 2016 experiment at four points. Sheath blight incidence was rated as the number of infected tillers divided by the total number of tillers per hill and used to calculate the area under the disease progress stairs (AUDPS). Sheath blight severity was rated on an unevenly spaced categorical scale and converted to the mid--point percentage value to calculate the AUDPS. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180)."}

@@

```{r fig-5, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) on sheath blight tiller incidence and tiller severity. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180)."}

@@

```{r fig-6, fig.cap="Posterior means and 95&nbsp;% credible intervals for the explanatory variables used in models of alternate wetting and drying irrigations (AWD) and N rate (NRTE) and the interaction of the two treatments on sheath blight leaf severity. Five different N treatments were applied to split plots depending on the experiment. In the 2015 experiment three N rate treatments were applied: no N (N0), 100&nbsp;kg&nbsp;/&nbsp;ha N (N100) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N120). In the 2016 experiment, two N rate treatments were applied: 60&nbsp;kg&nbsp;/&nbsp;ha N (N60) and 180&nbsp;kg&nbsp;/&nbsp;ha N (N180)."}
